Sampling requirements to detect ecosystem change

### 2020-10-07 R/supp_material.Rmd
addition to supp material of p-value explanation

The limits of our three sub-sampling functions are tied to the limits of the _e.divise()_ function. In a situation where the change is a linear change instead of a sudden changepoint, the function _e.divise()_ will find a changepoint in the middle of the linear decline (Fig. \ref{fig:caution1}). In such situation, iterative sampling still performs the best.

@@

>>>>

The limits of our three sub-sampling functions are tied to the limits of the _e.divise()_ function [@James2014]. In a situation where the change is a linear change instead of a sudden changepoint, the function _e.divise()_ will find a changepoint in the middle of the linear decline (Fig. \ref{fig:caution1}). In such situation, iterative sampling still performs the best.

@@

Finally, note that the p-values in the output of each functions are calculated within the function _e.divisive()_ (package _ecp_, @James2014). By default, the p-value of 0.005 means that no other permutation within the matrix lead to more energy needed to break the matrix. The p-value is in fact a frequency: only one configuration in 200 scenarios (initial matrix and 199 permutations) led to that much energy (1/200 = 0.005). We included in the three functions we coded (*sampling_random(), sampling_regular(), sampling_iterative()*) the arguments _R_ (default = 199) and _sig.lvl_ (default = 0.005), two arguments within the initial _e.divisive()_ function. By changing the default value, the user can choose a different number of permutation (if R = 19, then the minimum p-value will be 1/(1+19) = 0.05), and another significance level (if R = 199, the default, and the user wants to stop looking for changepoints once 10 configurations result in higher energy, then sig.lvl must be changed to 10/(1+199) = 0.05). Refer to the initial function for better understanding [@James2014].
